A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-01-11 JTB_supp/JTB_supp.Rmd
Fig S9 formatting

# Figure S9. Hysteresis under different nutrient and feeding regimes.
```{r FigS9, cache=T}
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)

@@

# Create plot
par(mfrow=c(2,2))

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
points(c(48,48,53,53), c(0.12,0.13,0.12,0.13), pch=c(19,1,19,1), cex=c(0.4,1,0.4,1), col=c("black","black","red","red"), xpd=T)
text(38, 0.125, labels="init. S:H", xpd=T, cex=0.7, srt=90)
text(46, c(0.12,0.13), labels=c("0.1", "0.0001"), xpd=T, pos=2, cex=0.7)
text(50, 0.15, labels=c("Steady state growth"), xpd=T, cex=0.7)
text(c(48,53), 0.14, labels=c("pos.", "neg."), xpd=T, cex=0.7)
apply(res1, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
apply(res2, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
apply(res3, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
apply(res4, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

dev.off()
```

>>>>

# Figure S9. Hysteresis under different nutrient and feeding regimes.
```{r FigS9, cache=T, fig.width=7, fig.height=7, echo=F, message=F}
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)

@@

# Create plot
par(mfrow=c(2,2), mar=c(3,3,1,1))

plot(NA, xlim=c(20,55), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
points(c(48,48,53,53), c(0.22,0.23,0.22,0.23), pch=c(19,1,19,1), cex=c(0.4,1,0.4,1), col=c("black","black","red","red"), xpd=T)
text(38, 0.225, labels="init. S:H", xpd=T, cex=0.7, srt=90)
text(46, c(0.22,0.23), labels=c("0.1", "0.0001"), xpd=T, pos=2, cex=0.7)
text(50, 0.25, labels=c("Steady state growth"), xpd=T, cex=0.7)
text(c(48,53), 0.24, labels=c("pos.", "neg."), xpd=T, cex=0.7)
apply(res1, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
apply(res2, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
apply(res3, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.3), xlab="Light", ylab="Steady state S:H ratio")
apply(res4, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

```
